A decision support tool for the Home Health Care Routing and Scheduling Problem

### 2022-02-25 tex/Paper/main.tex
updated CalculateJobTimes and FindValidTimes pseudocode to make sure all options are covered.
changes to pseudocode, swapped statements around.

\begin{algorithm}[h]
\footnotesize
\caption{\textsc{CalculateJobTimes}$(i, r_i)$}
\label{alg:cjt}
\begin{algorithmic}[1]
	\State Let $f$ be the initial shift for nurse $i$
	\State $a(i,k_{0}^i) \gets 0$
%	\For{$j \gets 1 \To m_i$}
	\For{$j \in r_i$}
		\State $a(i,j) \gets a(i, j-1) + w_{ij-1} + s_{j-1} + T_i(j-1, j)$
		\If{$j \in J'$}
			\State $j' \gets D(j)$ % D : J' -> DJ, returns other job in pair with job j
			\State $i' \gets NJ(j')$ % NJ : J -> N, returns the nurse assigned to the job j
			\If{$i$ appears later than $i'$ in $\mathcal{O}$}
				\State secondN $\gets \True$
			\EndIf
			\If{$(j, j') \in DS$}
				\State DS $\gets \True$
				\If{secondN $= \True \AAnd \tilde{a}(i,j) > t_{j'}$} %can also use l_j^(j'), latest ST allowed for j based on j'
					\Return feasible $\gets \False$
				\EndIf % arrival later than latest start time
			\Else 
				\State $DJ \gets \True$
				\If{secondN $= \True$} % This nurse is 2nd one to be assessed, other job has been done
				%Need to find out if this job j is before or after j' in the schedule
					\State $[t_{j'} + e_j^{(j')}, t_{j'} + l_j^{(j')}] \gets$ dependent time window, based on $t_{j'}$ set by $i'$
					\If{$\tilde{a}(i,j) > t_{j'} + l_j^{(j')} \AAnd$gap $= \False$} % current time is later than latest allowed start based on start time of j' and no gap tard allowed
						\Return feasible $\gets \False$
					\ElsIf{$\tilde{a}(i,j) > t_{j'} + l_{j}^{(j')} \AAnd$gap $= \True$}
						\If{$t_{j'} + l_{j}^{(j')} < t_{j'}$} %job j occurs before job j', gap too small
							\Return feasible $\gets \False$
						\EndIf
					\EndIf
				\EndIf % i appears later than i' in O
			\EndIf %(j, j') in DS
		\EndIf %if j in J'
		\If{$\max\{a(i,j), e_j\} + s_j > v(\pi_{f}^{i}) \AAnd f \neq g_i$}
			\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i,j,f, a(i,j)$)
			\If{feasible $= \False$}
				\Break
			\Else \hspace{0.2mm} \textbf{continue}
				%\Continue
			\EndIf
		\ElsIf{$a(i,j) > v(\pi_{f}^{i}) \AAnd a(i,j) < u(\pi_{f+1}^{i}) \AAnd f \neq g_i$}
			\State $v \gets v(\pi_{f}^{i})$
			\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i,j,f,v$)
			\If{feasible $= \False$}
				\Break
			\Else \hspace{0.2mm} \textbf{continue}
				%\Continue
			\EndIf
		\Else
			\State $w_{ij} \gets \max\{0, (e_j-a(i,j))\}$
			\State $z_j \gets \max\{0, (a(i,j) - l_j)\}$
			\State $t_j \gets a(i,j) + w_{ij}$
		\EndIf
	\EndFor
	\Return either statement of infeasibility or feasible schedule for nurse $i$
\end{algorithmic}
\end{algorithm}

@@

\caption{\textsc{FindValidTime($i, j, f, a(i,j)$)}}

@@

	\State feasible $\gets \False$, DJ $\gets \False$, DS $\gets \False$, secondN $\gets \False$, gap $\gets \False$

@@

	\If{$j \in J'$}
		\State $j' \gets D(j)$ % D : J' -> DJ, returns other job in pair with job j
		\State $i' \gets NJ(j')$ % NJ : J -> N, returns the nurse assigned to the job j
		\If{$i$ appears later than $i'$ in $\mathcal{O}$}
			\State secondN $\gets \True$

@@

		\If{$(j, j') \in DS$}
			\State DS $\gets \True$
				\If{secondN $= \True \AAnd \tilde{a}(i,j) > t_{j'}$} %can also use l_j^(j'), latest ST allowed for j based on j'
				\EndIf % arrival later than latest start time
			\State $DJ \gets \True$
			%\If{secondN $= \False$}
			%	\State original TWs are used
			\If{secondN $= \True$} % This nurse is the 2nd one to be assessed, other job has been done
				%Need to find out if this job j is before or after j' in the schedule
				%\State $[e_j^{(j')}, l_j^{(j')}] \gets$ dependent time window, based on $t_{j'}$ set by $i'$
				\If{$\tilde{a}(i,j) > t_{j'} + l_j^{(j')} \AAnd$gap $= \False$} % current time is later than latest allowed start based on start time of j' and no gap tard allowed
				\ElsIf{$\tilde{a}(i,j) > t_{j'} + l_{j}^{(j')} \AAnd$gap $= \True$}
					\If{$t_{j'} + l_{j}^{(j')} < t_{j'}$} %job j occurs before job j', gap too small
			\EndIf % i appears later than i' in O
		\EndIf %(j, j') in DS
	\EndIf %if j in J'

>>>>

\begin{algorithm}[htbp!]
\scriptsize
\caption{\textsc{CalculateJobTimes}$(i, r_i)$}
\label{alg:cjt}
\begin{algorithmic}[1]
	\State feasible $\gets \False$
	\State Let $f$ be the initial shift for nurse $i$
	\State $a(i,k_{0}^i) \gets 0$
%	\For{$j \gets 1 \To m_i$}
	\For{$j \in r_i$}
		\State $a(i,j) \gets a(i, j-1) + w_{ij-1} + s_{j-1} + T_i(j-1, j)$
		\State $i' \gets \Null$, $j' \gets \Null$
		\State DJ $\gets \False$
		\State DS $\gets \False$
		\State secondN $\gets \False$
		\If{$j \in J'$}
			\State $j' \gets D(j)$ % D : J' -> DJ, returns other job in pair with job j
			\State $i' \gets NJ(j')$ % NJ : J -> N, returns the nurse assigned to the job j
			\If{$i$ appears later than $i'$ in $\mathcal{O}$}
				\State secondN $\gets \True$
			\EndIf
			\If{$(j, j') \in DS$}
				\State DS $\gets \True$
				\If{secondN $= \True \AAnd a(i,j) > t_{j'}$} %can also use l_j^(j'), latest ST allowed for j based on j'
					\State feasible $\gets \False$
					\Break
				\EndIf % arrival later than latest start time
			\Else 
				\State $DJ \gets \True$
				\If{secondN $= \True$} % This nurse is 2nd one to be assessed, other job has been done
				%Need to find out if this job j is before or after j' in the schedule
					\State $[t_{j'} + e_j^{(j')}, t_{j'} + l_j^{(j')}] \gets$ dependent time window, based on $t_{j'}$ set by $i'$
					\If{$a(i,j) > t_{j'} + l_j^{(j')} \AAnd$gap $= \False$} % current time is later than latest allowed start based on start time of j' and no gap tard allowed
						\State feasible $\gets \False$
						\Break
					\ElsIf{$a(i,j) > t_{j'} + l_{j}^{(j')} \AAnd$gap $= \True$}
						\If{$t_{j'} + l_{j}^{(j')} < t_{j'}$} %job j occurs before job j', gap too small
							\State feasible $\gets \False$
							\Break
						\EndIf
					\EndIf
				\EndIf % i appears later than i' in O
			\EndIf %(j, j') in DS
		\EndIf %if j in J'
		\If{$a(i,j) > v(\pi_{f}^{i}) \AAnd a(i,j) < u(\pi_{f+1}^{i}) \AAnd f \neq g_i$}
			\State $v \gets v(\pi_{f}^{i})$
			\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i, j, f, v, i', j'$, DS, DJ, secondN)
			\If{feasible $= \False$}
				\Break
			\Else \hspace{0.2mm} \textbf{continue}
				%\Continue
			\EndIf
		\ElsIf{$\max\{a(i,j), e_j\} + s_j > v(\pi_{f}^{i}) \AAnd f \neq g_i$}
			\State feasible, $t_j, w_{ij}, z_j, \tilde{z}_j, f \gets$ \textsc{FindValidTime}($i, j, f, a(i,j), i', j'$, DS, DJ, secondN)
			\If{feasible $= \False$}
				\Break
			\Else \hspace{0.2mm} \textbf{continue}
				%\Continue
			\EndIf
		\Else
			\State $w_{ij} \gets \max\{0, (e_j-a(i,j))\}$
			\State $z_j \gets \max\{0, (a(i,j) - l_j)\}$
			\State $t_j \gets a(i,j) + w_{ij}$
		\EndIf
	\EndFor
	\Return either statement of infeasibility or feasible schedule for nurse $i$
\end{algorithmic}
\end{algorithm}

@@

\caption{\textsc{FindValidTime}($i, j, f, a(i,j), i', j'$, DS, DJ, secondN, gap)}

@@

	\State feasible $\gets \False$

@@

	\If{DJ $= \True \Or$DS $= \True$}

@@

%	\If{$j \in J'$}
%		\State $j' \gets D(j)$ % D : J' -> DJ, returns other job in pair with job j
%		\State $i' \gets NJ(j')$ % NJ : J -> N, returns the nurse assigned to the job j
%		\If{$i$ appears later than $i'$ in $\mathcal{O}$}
%			\State secondN $\gets \True$
%		\EndIf
%		\If{$(j, j') \in DS$}
%			\State DS $\gets \True$
%				\If{secondN $= \True \AAnd \tilde{a}(i,j) > t_{j'}$} %can also use l_j^(j'), latest ST allowed for j based on j'
%					%\State valid $\gets \False$
%					%\Return infeasible
%					\Return feasible $\gets \False$
%				\EndIf % arrival later than latest start time
%		\Else 
%			\State $DJ \gets \True$
%			%\If{secondN $= \False$}
%			%	\State original TWs are used
%			\If{secondN $= \True$} % This nurse is the 2nd one to be assessed, other job has been done
%				%Need to find out if this job j is before or after j' in the schedule
%				%\State $[e_j^{(j')}, l_j^{(j')}] \gets$ dependent time window, based on $t_{j'}$ set by $i'$
%				\State $[t_{j'} + e_j^{(j')}, t_{j'} + l_j^{(j')}] \gets$ dependent time window, based on $t_{j'}$ set by $i'$
%				%\If{$\tilde{a}(i,j) > l_j^{(j')} \AAnd$gap $= \False$}
%				\If{$\tilde{a}(i,j) > t_{j'} + l_j^{(j')} \AAnd$gap $= \False$} % current time is later than latest allowed start based on start time of j' and no gap tard allowed
%					%\State valid $\gets \False$
%					%\Return infeasible
%					\Return feasible $\gets \False$
%				\ElsIf{$\tilde{a}(i,j) > t_{j'} + l_{j}^{(j')} \AAnd$gap $= \True$}
%					\If{$t_{j'} + l_{j}^{(j')} < t_{j'}$} %job j occurs before job j', gap too small
%						\Return feasible $\gets \False$
%					\EndIf
%				\EndIf
%			\EndIf % i appears later than i' in O
%		\EndIf %(j, j') in DS
%	\EndIf %if j in J'
